% ABSOLUTE COORDINATE ENGINE: Uses {textpos} package for pixel-perfect positioning
\documentclass{cal-pleading}

\begin{document}

\makecaption
{NUHA SAYEGH\\5132 Rosemead Blvd.\\San Gabriel, CA 91776\\(626) 348-3039\\ \\ \textbf{NUHA SAYEGH, IN PRO PER}}
{NUHA SAYEGH}
{H. BUI LAW FIRM}
{[ASSIGNED BY LACBA]}
{STATEMENT OF DISPUTE}

\begin{center} \textbf{I. THE DUTY: LOYALTY AND COMPETENCE} \end{center}
The Attorney owed the Client a duty of undivided loyalty (Rules of Professional Conduct, Rule 1.7) and competent representation (Rule 1.1). This mandated prioritizing the Client's critical hearing over the Attorney's personal scheduling conveniences.

\begin{center} \textbf{II. THE BREACH: THE CHATSWORTH CONFLICT} \end{center}
On November 17, 2025, Associate Attorney Sara Memari advised the Client to appear remotely for the contested November 19 evidentiary hearing.

As documented in \textbf{Exhibit C (Contemporaneous Detailed Meeting Notes)}, this advice was not strategic but self-interested. Ms. Memari disclosed that she had a conflicting in-person appearance at the Chatsworth Courthouse (the ``Chatsworth Conflict') and could not appear in person for the Client. She stated, per the memorialized notes: ``I'm supposed to appear in Chatsworth... so I'll have to, unfortunately, appear remotely.'

\begin{center} \textbf{III. THE CAUSATION: DENIAL OF TESTIMONY} \end{center}
The harm was immediate and direct. On November 19, 2025, the Court denied the Client's request for the ``Exclusive Use of Home' order. As confirmed by Exhibit E, the Court refused to hear the Client's testimony specifically because she was not present in the courtroom.

\begin{center} \textbf{IV. REMEDY SOUGHT} \end{center}
The Client has received a partial refund. However, the remaining fees of \textbf{\$2,969.77} represent the cost of a failed strategy driven by an ethical violation. The Client demands full disgorgement of this remaining balance.

\vspace{24bp}
I declare under penalty of perjury under the laws of the State of California that the foregoing is true and correct. Executed on December 12, 2025, at San Gabriel, California.

\vspace{36bp}
\noindent\rule{3in}{0.5pt}\\
NUHA SAYEGH, Client/Petitioner

\end{document}
