% ═══════════════════════════════════════════════════════════════════════════════
% EXHIBIT E - Demand Letter to Nicora Law Offices
% Case No. 25PR000590 - Estate of Judy Brakebill Jones
% December 3, 2025
% ═══════════════════════════════════════════════════════════════════════════════

\documentclass[12pt,letterpaper]{article}

% GEOMETRY
\usepackage[top=1in,bottom=1in,left=1in,right=1in,headheight=36pt,footskip=0.5in]{geometry}

% FONTS
\usepackage{fontspec}
\setmainfont{Times New Roman}[Ligatures=TeX]

% LINE SPACING
\usepackage{setspace}
\onehalfspacing

% COLORS
\usepackage{xcolor}
\definecolor{NavyHeader}{HTML}{1A2B4C}
\definecolor{BatesGray}{HTML}{666666}

% HEADERS AND FOOTERS
\usepackage{fancyhdr}
\usepackage{lastpage}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\small Exhibit E\\Case No. 25PR000590\\Page \thepage\ of \pageref{LastPage}}
\fancyfoot[C]{\small\textit{Confidential -- Produced in Litigation}}
\fancyfoot[R]{\scriptsize\color{BatesGray}EBJ-25PR000590-0500\ifnum\value{page}<10 0\fi\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\fancypagestyle{firstpage}{
    \fancyhf{}
    \renewcommand{\headrulewidth}{0pt}
    \fancyfoot[C]{\small\textit{Confidential -- Produced in Litigation}}
    \fancyfoot[R]{\scriptsize\color{BatesGray}EBJ-25PR000590-050001}
    \renewcommand{\footrulewidth}{0.4pt}
}

% PDF SETUP
\usepackage[hidelinks]{hyperref}
\hypersetup{
    pdftitle={Exhibit E - Demand Letter - Case 25PR000590},
    pdfauthor={Eric Brakebill Jones},
    pdfsubject={Estate of Judy Brakebill Jones}
}

% UTILITIES
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{enumitem}

\begin{document}
\thispagestyle{firstpage}

% ═══════════════════════════════════════════════════════════════════════════════
% EXHIBIT HEADER
% ═══════════════════════════════════════════════════════════════════════════════

\begin{center}
\rule{\textwidth}{2pt}\\[0.5em]
{\Large\bfseries EXHIBIT E}\\[0.5em]
{\large Demand Letter to Nicora Law Offices, LLP}\\[0.3em]
{\normalsize Formal Demand for Withdrawal of Petition}\\[0.3em]
{\normalsize December 3, 2025}\\[0.5em]
\rule{\textwidth}{2pt}
\end{center}

\vfill
\begin{center}
{\itshape See attached letter on following page}
\end{center}
\vfill

\newpage

% ═══════════════════════════════════════════════════════════════════════════════
% LETTERHEAD
% ═══════════════════════════════════════════════════════════════════════════════

\begin{center}
\rule{\textwidth}{2pt}\\[0.5em]
{\large\bfseries ERIC BRAKEBILL JONES}\\[0.3em]
{\scshape Sole Successor Trustee}\\
{\itshape Judy Brakebill Jones 2008 Revocable Trust}\\[0.5em]
5634 Noel Drive\\
Temple City, CA 91780\\
(626) 348-3019\\
eric@recovery-compass.org\\[0.5em]
\rule{\textwidth}{2pt}
\end{center}

\vspace{1em}

\hfill December 3, 2025

\vspace{1em}

\noindent\textbf{VIA CERTIFIED MAIL AND EMAIL}

\vspace{0.5em}

\noindent Albert J. Nicora, Esq.\\
Jacqueline E. Nicora, Esq.\\
Nicora Law Offices, LLP\\
26385 Carmel Rancho Boulevard, Suite 100\\
Carmel, CA 93923

\vspace{1em}

\noindent\hspace{0.5in}\textbf{Re: Demand for Immediate Withdrawal of Petition;}\\
\hspace{0.75in}\textbf{Notice of Bad Faith Contest}\\
\hspace{0.75in}\textbf{Case No. 25PR000590 -- Estate of Judy Brakebill Jones}

\vspace{1em}

\noindent Dear Mr. Nicora and Ms. Nicora:

\vspace{0.5em}

\hspace{0.5in}I write as Sole Successor Trustee of the Judy Brakebill Jones 2008 Revocable Trust to demand the immediate withdrawal of the Petition for Probate of Lost Will filed by your client, Heidi Marichen Jones Blanchard.

\hspace{0.5in}Your client's petition is verified under penalty of perjury. It claims the Will is ``lost'' and that the identity of the Executor is unknown. \textbf{THIS IS A DIRECT FALSEHOOD.} I am in possession of irrefutable evidence proving your client has been in possession of the Will since April 2025 and explicitly recognized my authority as Executor in May 2025.

\hspace{0.5in}Proceeding with this fraudulent petition constitutes a direct contest of the Trust without probable cause, triggering the No-Contest Clause (Trust Section XIV.E). This will result in your client's immediate and total disinheritance.

\vspace{1em}

% ═══════════════════════════════════════════════════════════════════════════════
% SECTION I
% ═══════════════════════════════════════════════════════════════════════════════

\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}\\[0.3em]
{\large\bfseries\textcolor{NavyHeader}{I. EVIDENCE OF PERJURY: THE MAY 19 ADMISSION}}\\[0.3em]
\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}

\vspace{0.5em}

\hspace{0.5in}Your client's filing claims she does not know who the Executor is. However, on May 19, 2025, the day after our mother's funeral, your client met with me at the Salinas property. During this meeting, she did not merely ``know'' I was the Executor; she instructed me to act in that capacity.

\hspace{0.5in}This meeting was documented by a third-party witness, Nuha Sayegh. Your client cannot claim an expectation of privacy regarding this conversation because she explicitly requested that Ms. Sayegh take notes of the discussion. At the start of the meeting, your client asked: ``Nuha, are you writing notes? I think it would be helpful.''

\hspace{0.5in}According to the contemporaneous written log created at your client's request:

\begin{itemize}[leftmargin=1in]
    \item \textbf{The Admission:} When I asked, ``Mom chose me to be the executor. Is that a fact?'' Your client responded: \textbf{``Yeah, okay.''}

    \item \textbf{The Instruction:} Moments later, your client explicitly directed me: \textbf{``So the first thing that you need to do as the executor, you need to start the probate process.''}
\end{itemize}

\hspace{0.5in}Your client cannot instruct me to act ``as the executor'' in May and then swear to the Court in November that the Executor is unknown. \textbf{This constitutes FRAUD ON THE COURT.}

\vspace{1em}

% ═══════════════════════════════════════════════════════════════════════════════
% SECTION II
% ═══════════════════════════════════════════════════════════════════════════════

\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}\\[0.3em]
{\large\bfseries\textcolor{NavyHeader}{II. PREMEDITATED SPOLIATION: THE iPHONE}}\\[0.3em]
\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}

\vspace{0.5em}

\hspace{0.5in}Your client's retention of the decedent's iPhone was a calculated act of spoliation. Witness testimony confirms that on May 19, your client specifically requested time to manipulate the device before surrendering it.

\begin{itemize}[leftmargin=1in]
    \item \textbf{The Request for Access:} Your client stated: \textbf{``I just need it for a couple more days access. I don't need to have it.''}

    \item \textbf{The Act:} Two days later, on May 21, 2025---exactly the ``couple more days'' she requested---she handed me a ``decoy'' iPhone that had been wiped of critical data.
\end{itemize}

\hspace{0.5in}This sequence proves your client utilized those ``couple days'' to alter the evidence before providing a fraudulent device to the Trustee. This willful spoliation blocks access to 2FA codes required for Trust administration.

\vspace{1em}

% ═══════════════════════════════════════════════════════════════════════════════
% SECTION III
% ═══════════════════════════════════════════════════════════════════════════════

\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}\\[0.3em]
{\large\bfseries\textcolor{NavyHeader}{III. BAD FAITH ASSET CONVERSION (DOUBLE DAMAGES)}}\\[0.3em]
\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}

\vspace{0.5em}

\hspace{0.5in}Your client knowingly converted Trust assets (a 2013 Mercedes-Benz) despite acknowledging she lacked the authority to do so.

\begin{itemize}[leftmargin=1in]
    \item \textbf{Premeditation:} On May 19, your client admitted to listing the car for sale immediately: ``We just put it for sale on Craigslist for 11,000\ldots\ I don't know if you, if you don't agree, we can take it off.''

    \item \textbf{The Act:} Despite acknowledging she needed my agreement (``if you don't agree''), she sold the vehicle anyway without my consent. Your own letter dated June 27, 2025, confirms the sale and your client's possession of \textbf{\$10,650.00} in proceeds.
\end{itemize}

\hspace{0.5in}This willful misappropriation satisfies the standard for \textbf{DOUBLE DAMAGES} under \textbf{California Probate Code \S~859}, creating a liability of \textbf{\$21,300.00}.

\hspace{0.5in}California courts have consistently held that double damages under Probate Code \S~859 are available when a person wrongfully takes trust property, particularly in cases involving elder financial abuse. In \textit{Keading v. Keading} (2021) 60 Cal.App.5th 1115, the Court of Appeal confirmed that a separate finding of bad faith is not required when the taking constitutes elder or dependent adult financial abuse. Your client's willful conversion of the Mercedes-Benz, after acknowledging she needed the Trustee's consent, satisfies this standard.

\vspace{1em}

% ═══════════════════════════════════════════════════════════════════════════════
% SECTION IV
% ═══════════════════════════════════════════════════════════════════════════════

\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}\\[0.3em]
{\large\bfseries\textcolor{NavyHeader}{IV. THE ULTIMATUM: NO-CONTEST CLAUSE ENFORCEMENT}}\\[0.3em]
\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}

\vspace{0.5em}

\hspace{0.5in}Your client's petition is a direct contest filed without probable cause. She knew the Will existed; she knew I was Executor; and she admitted on May 19 that creditors told her ``the trust can't tell you anything'' without proper authority.

\hspace{0.5in}To avoid the immediate filing of an Objection, Cross-Petition for Disinheritance, and referral for Perjury, your client must:

\begin{enumerate}[leftmargin=1in]
    \item \textbf{WITHDRAW} the Petition for Probate (Case No. 25PR000590) immediately, with prejudice.

    \item \textbf{RETURN} the \textbf{\$10,650.00} illicit proceeds from the Mercedes sale plus the \textbf{\$335.00} from garage sales (\textbf{\$10,985.00 total}).

    \item \textbf{SURRENDER} the decedent's authentic iPhone and the key to the Wells Fargo Safe Deposit Box.
\end{enumerate}

\vspace{1em}

\begin{center}
\fbox{\parbox{5in}{\centering\large\bfseries DEADLINE: You have \underline{10 days} from the date of this letter.}}
\end{center}

\vspace{1em}

\begin{center}
{\Large\bfseries GOVERN YOURSELVES ACCORDINGLY.}
\end{center}

\vspace{2em}

\hfill Respectfully submitted,

\vspace{2em}

\hfill\rule{3in}{0.4pt}\\
\hfill\textbf{ERIC BRAKEBILL JONES}\\
\hfill Successor Trustee\\
\hfill Judy Brakebill Jones 2008 Revocable Trust

\vspace{2em}

\noindent\textbf{Enclosures:}
\begin{itemize}[leftmargin=0.5in, label={}]
    \item Exhibit A: Jonelle Beck Email (April 8, 2025)
    \item Exhibit B: SMS Messages \& Trust Documents (April 7, 2025)
    \item Exhibit C: Nicora Law Letter (June 27, 2025)
    \item Exhibit D: Declaration of Nuha Sayegh (December 3, 2025)
\end{itemize}

% ═══════════════════════════════════════════════════════════════════════════════
% END OF EXHIBIT
% ═══════════════════════════════════════════════════════════════════════════════

\vfill

\begin{center}
\rule{3in}{1pt}\\[0.5em]
{\bfseries END OF EXHIBIT E}\\[0.3em]
\rule{3in}{1pt}
\end{center}

\end{document}
