% ═══════════════════════════════════════════════════════════════════════════════
% EXHIBIT C - Nicora Law Letter
% Case No. 25PR000590 - Estate of Judy Brakebill Jones
% June 27, 2025
% ═══════════════════════════════════════════════════════════════════════════════

\documentclass[12pt,letterpaper]{article}

% GEOMETRY
\usepackage[top=1in,bottom=1in,left=1in,right=1in,headheight=36pt,footskip=0.5in]{geometry}

% FONTS
\usepackage{fontspec}
\setmainfont{Times New Roman}[Ligatures=TeX]

% LINE SPACING
\usepackage{setspace}
\onehalfspacing

% COLORS
\usepackage{xcolor}
\definecolor{NavyHeader}{HTML}{1A2B4C}
\definecolor{BatesGray}{HTML}{666666}

% HEADERS AND FOOTERS
\usepackage{fancyhdr}
\usepackage{lastpage}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\small Exhibit C\\Case No. 25PR000590\\Page \thepage\ of \pageref{LastPage}}
\fancyfoot[C]{\small\textit{Confidential -- Produced in Litigation}}
\fancyfoot[R]{\scriptsize\color{BatesGray}EBJ-25PR000590-0300\ifnum\value{page}<10 0\fi\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\fancypagestyle{firstpage}{
    \fancyhf{}
    \renewcommand{\headrulewidth}{0pt}
    \fancyfoot[C]{\small\textit{Confidential -- Produced in Litigation}}
    \fancyfoot[R]{\scriptsize\color{BatesGray}EBJ-25PR000590-030001}
    \renewcommand{\footrulewidth}{0.4pt}
}

% PDF SETUP
\usepackage[hidelinks]{hyperref}
\hypersetup{
    pdftitle={Exhibit C - Nicora Law Letter - Case 25PR000590},
    pdfauthor={Eric Brakebill Jones},
    pdfsubject={Estate of Judy Brakebill Jones}
}

% UTILITIES
\usepackage{graphicx}
\usepackage{parskip}

\begin{document}
\thispagestyle{firstpage}

% ═══════════════════════════════════════════════════════════════════════════════
% EXHIBIT HEADER
% ═══════════════════════════════════════════════════════════════════════════════

\begin{center}
\rule{\textwidth}{2pt}\\[0.5em]
{\Large\bfseries EXHIBIT C}\\[0.5em]
{\large Letter from Nicora Law Offices, LLP}\\[0.3em]
{\normalsize Opposing Counsel's Acknowledgment of Vehicle Sale}\\[0.3em]
{\normalsize June 27, 2025}\\[0.5em]
\rule{\textwidth}{2pt}
\end{center}

\vspace{2em}

% ═══════════════════════════════════════════════════════════════════════════════
% LETTERHEAD
% ═══════════════════════════════════════════════════════════════════════════════

\begin{center}
\rule{\textwidth}{0.5pt}\\[1em]

{\large\bfseries NICORA LAW OFFICES, LLP}\\[0.3em]
{\scshape Attorneys at Law}\\[1em]

26385 Carmel Rancho Blvd., Suite 100\\
Carmel, California 93923\\[0.5em]

Telephone: (831) 622-2000\\
Facsimile: (831) 622-2001\\
www.nicoralaw.com\\[1em]

\rule{\textwidth}{0.5pt}
\end{center}

\vspace{0.5em}

\begin{tabbing}
\hspace{3in}\=\kill
\textbf{ALBERT J. NICORA} \> \textbf{OF COUNSEL:}\\
\> Jacqueline E. Nicora\\
\> Michael A. Atteridge\\
\> Joelle C. Clark\\
\> Andrew S. Blomquist\\
\> Barry R. Harrow\\
\end{tabbing}

\vspace{1em}

\hfill June 27, 2025

\vspace{1em}

\noindent Eric Jones\\
5634 Noel Drive\\
Temple City, CA 91780

\vspace{1em}

\noindent\hspace{0.5in}\textbf{Re: The Judy Brakebill Jones 2008 Revocable Trust}\\
\hspace{0.75in}\textbf{Last Will of Judy Brakebill Jones}

\vspace{1em}

\noindent Dear Mr. Jones:

\vspace{0.5em}

\hspace{0.5in}This office represents Heidi Blanchard who is a beneficiary of the Judy Brakebill Jones 2008 Revocable Trust and Co-Executor of the Last Will of Judy Brakebill Jones.

\hspace{0.5in}Please direct all communications for our client directly to this office. Do not contact our client directly.

\hspace{0.5in}We have been able to review the following documents:

\begin{enumerate}
    \item Last Will of Judy Brakebill Jones dated April 8, 2008
    \item The Judy Brakebill Jones 2008 Revocable Trust dated March 18, 2008
    \item First Amendment to the Judy Brakebill Jones 2008 Revocable Trust dated August 1, 2016
\end{enumerate}

\hspace{0.5in}If there are any amendments, codicils, or other relevant estate planning documents, please provide us with a copy.

\hspace{0.5in}We must state that we dispute the multiple characterizations of our client and other family members stated by you. In an effort to move the process forward, we will not respond to your specific claims at this time.

\hspace{0.5in}\textbf{Heidi, as Co-Executor, sold tangible personal property including a vehicle.} Under the Last Will, all tangible personal property including personal automobiles is to be distributed to Judy's children equally. Therefore, my client proposes \textbf{the \$10,650.00 from the sale of the tangible personal property} be distributed equally between you, Gretchen, and Heidi. Each would receive \$3,550.00.

\hspace{0.5in}Please advise us if you are in agreement. Please confirm your check should be sent to your attention at the address above.

\newpage

\noindent Eric Jones\\
June 27, 2025\\
Re: Judy Brakebill Jones, deceased\\
Page 2

\vspace{1em}

\hspace{0.5in}Regarding the remaining tangible personal property including items in the safe deposit box, please contact us to discuss the next steps including accessing the safe deposit box and distributing its contents. We can also discuss distributing the remaining personal property.

\hspace{0.5in}Regarding the Judy Brakebill Jones 2008 Revocable Trust, please provide us with the following:

\begin{enumerate}
    \item A list of assets as of date of death.
    \item Your plan regarding the real property located at 17742 Berta Canyon Road, Salinas, CA 93907.
    \begin{enumerate}
        \item[a.] Specifically: we request being advised as to who do you plan on listing the property with and your proposed listing price.
    \end{enumerate}
\end{enumerate}

\hspace{0.5in}Again, all communication regarding the Trust or assets of Judy Brakebill Jones should be directed to our office. Please do not contact our client.

\hspace{0.5in}We look forward to working with you on this matter.

\vspace{1em}

\noindent Thank you,

\vspace{1.5em}

\noindent\textbf{NICORA LAW OFFICES, LLP}

\vspace{1.5em}

\noindent Albert J. Nicora

% ═══════════════════════════════════════════════════════════════════════════════
% END OF EXHIBIT
% ═══════════════════════════════════════════════════════════════════════════════

\vfill

\begin{center}
\rule{3in}{1pt}\\[0.5em]
{\bfseries END OF EXHIBIT C}\\[0.3em]
\rule{3in}{1pt}
\end{center}

\end{document}
