% ═══════════════════════════════════════════════════════════════════════════════
% EXHIBIT B - SMS Messages & Estate Planning Documents
% Case No. 25PR000590 - Estate of Judy Brakebill Jones
% April 7, 2025
% ═══════════════════════════════════════════════════════════════════════════════

\documentclass[12pt,letterpaper]{article}

% GEOMETRY
\usepackage[top=1in,bottom=1in,left=1in,right=1in,headheight=36pt,footskip=0.5in]{geometry}

% FONTS
\usepackage{fontspec}
\setmainfont{Times New Roman}[Ligatures=TeX]

% LINE SPACING
\usepackage{setspace}
\onehalfspacing

% COLORS
\usepackage{xcolor}
\definecolor{NavyHeader}{HTML}{1A2B4C}
\definecolor{BatesGray}{HTML}{666666}
\definecolor{SMSEricBg}{HTML}{E8F5E9}
\definecolor{SMSHeidiBg}{HTML}{F5F5F5}
\definecolor{SMSBorder}{HTML}{CCCCCC}

% HEADERS AND FOOTERS
\usepackage{fancyhdr}
\usepackage{lastpage}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\small Exhibit B\\Case No. 25PR000590\\Page \thepage\ of \pageref{LastPage}}
\fancyfoot[C]{\small\textit{Confidential -- Produced in Litigation}}
\fancyfoot[R]{\scriptsize\color{BatesGray}EBJ-25PR000590-0200\ifnum\value{page}<10 0\fi\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\fancypagestyle{firstpage}{
    \fancyhf{}
    \renewcommand{\headrulewidth}{0pt}
    \fancyfoot[C]{\small\textit{Confidential -- Produced in Litigation}}
    \fancyfoot[R]{\scriptsize\color{BatesGray}EBJ-25PR000590-020001}
    \renewcommand{\footrulewidth}{0.4pt}
}

% PDF SETUP
\usepackage[hidelinks]{hyperref}
\hypersetup{
    pdftitle={Exhibit B - SMS Messages - Case 25PR000590},
    pdfauthor={Eric Brakebill Jones},
    pdfsubject={Estate of Judy Brakebill Jones}
}

% UTILITIES
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{tcolorbox}
\tcbuselibrary{skins}

% SMS MESSAGE BOXES
\newtcolorbox{smsheidi}{
    colback=SMSHeidiBg,
    colframe=SMSBorder,
    width=0.75\textwidth,
    left=5pt,
    right=5pt,
    top=5pt,
    bottom=5pt,
    boxrule=0.5pt,
    arc=5pt
}

\newtcolorbox{smseric}{
    colback=SMSEricBg,
    colframe=SMSBorder,
    width=0.75\textwidth,
    left=5pt,
    right=5pt,
    top=5pt,
    bottom=5pt,
    boxrule=0.5pt,
    arc=5pt
}

\begin{document}
\thispagestyle{firstpage}

% ═══════════════════════════════════════════════════════════════════════════════
% EXHIBIT HEADER
% ═══════════════════════════════════════════════════════════════════════════════

\begin{center}
\rule{\textwidth}{2pt}\\[0.5em]
{\Large\bfseries EXHIBIT B}\\[0.5em]
{\large SMS Text Messages \& Estate Planning Documents}\\[0.3em]
{\normalsize Demonstrating Co-Executor Acknowledgment}\\[0.3em]
{\normalsize April 7, 2025}\\[0.5em]
\rule{\textwidth}{2pt}
\end{center}

\vspace{1.5em}

% ═══════════════════════════════════════════════════════════════════════════════
% PART 1: SMS TRANSCRIPT
% ═══════════════════════════════════════════════════════════════════════════════

\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}\\[0.3em]
{\large\bfseries\textcolor{NavyHeader}{PART 1: SMS TEXT MESSAGE TRANSCRIPT}}\\[0.3em]
\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}

\vspace{1em}

\begin{center}
\fbox{\parbox{4in}{
\centering
\textbf{Heidi (Eric B Jones' Sister)}\\
Heidi Cellphone: (530) 513-9710\\
\textit{iPhone Messages -- April 7, 2025}
}}
\end{center}

\vspace{1.5em}

% Message 1
\noindent\textit{April 7, 2025 -- 1:25 PM}
\begin{smsheidi}
\textbf{Heidi:} Eric, I really need to talk to you. Can you call me?
\end{smsheidi}

\vspace{1em}

% Message 2
\hfill\textit{April 7, 2025 -- 1:42 PM}
\begin{flushright}
\begin{smseric}
\textbf{Eric:} If you do that then this is going to feel a lot easier and doable right now. I promise you Heidi. Let me help and make this easier for you. This is me waving my arms in the air saying ``I can help I can help I can help!! Please let me
\end{smseric}
\end{flushright}

\vspace{1em}

% Document transmission
\noindent\textit{April 7, 2025 -- 1:43 PM}
\begin{smsheidi}
\textbf{Heidi:} [Heidi transmits photographs of estate planning documents via SMS -- see Part 2 below for document contents]
\end{smsheidi}

\vspace{1em}

% Message 3
\hfill\textit{April 7, 2025 -- 1:46 PM}
\begin{flushright}
\begin{smseric}
\textbf{Eric:} Is that all of them?
\end{smseric}
\end{flushright}

\vspace{0.5em}

\begin{flushright}
\begin{smseric}
\textbf{Eric:} Now send an audio recording or text or message summarizing everything you just told me on the phone and I'll have an answer for you within 20 minutes
\end{smseric}
\end{flushright}

\vspace{1em}

% Message 4 - CRITICAL
\noindent\textit{April 7, 2025 -- 1:50 PM}
\begin{smsheidi}
\textbf{Heidi:} OK, so the problem looks like we are co-power of attorneys but on one piece of paper \textbf{it says that you are a successor trustee and if you are unable to be successor trustee then Heidi Jones Blanchard she serve} so in that one your name is first, but in other ones, my name is first and in some we are combined
\end{smsheidi}

\vspace{0.5em}

\begin{smsheidi}
\textbf{Heidi:} Also, the problem is, I don't know who wrote this will what attorney wrote it
\end{smsheidi}

\vspace{0.5em}

\begin{smsheidi}
\textbf{Heidi:} I just left a message with Stephanie to see who her dad's attorney was because I imagine that Mom and Larry used the same one
\end{smsheidi}

\vspace{1em}

% Message 5
\hfill\textit{April 7, 2025 -- 1:52 PM}
\begin{flushright}
\begin{smseric}
\textbf{Eric:} Ok perfect. and when is this meeting you're going to have next and with who exactly and what questions will they likely ask?
\end{smseric}
\end{flushright}

\newpage

% ═══════════════════════════════════════════════════════════════════════════════
% PART 2: DOCUMENT EXCERPTS
% ═══════════════════════════════════════════════════════════════════════════════

\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}\\[0.3em]
{\large\bfseries\textcolor{NavyHeader}{PART 2: ESTATE PLANNING DOCUMENTS TRANSMITTED VIA SMS}}\\[0.3em]
\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}

\vspace{1em}

\noindent\textit{The following documents were photographed by Heidi Blanchard and transmitted to Eric Jones via SMS on April 7, 2025, demonstrating that Heidi was in possession of the complete estate planning documents within days of the decedent's passing.}

\vspace{1.5em}

% Document A
\noindent\rule{\textwidth}{0.5pt}\\[0.3em]
{\bfseries Document B-1: Springing Durable Power of Attorney for Finances}\\[0.3em]
\rule{\textwidth}{0.5pt}

\vspace{0.5em}

\begin{center}
\fbox{\parbox{5.5in}{
\centering
\textbf{SPRINGING DURABLE POWER OF ATTORNEY FOR FINANCES}\\
FOR JUDY BRAKEBILL JONES\\
AKA JUDY LEE BRAKEBILL JONES\\
AKA JUDY BRAKEBILL JONES LASHER\\
AKA JUDY LEE JONES
}}
\end{center}

\vspace{0.5em}

\noindent\textit{Key Provision (Page 2):}

\begin{quote}
``LEE JONES, of Monterey County, California, appoint my children, \textbf{HEIDI JONES (530-864-6272) and ERIC JONES (530-219-2364), as my co-attorneys-in-fact} to manage my affairs. If I revoke my attorney-in-fact's authority, or if my attorney-in-fact is not willing, able, or reasonably available to act on my behalf, I designate as follows:

\textbf{First Alternate Agent: LAWRENCE ELLIOT LASHER (650) 248-7995.}''
\end{quote}

\vspace{0.5em}
\noindent\textit{Notarization: April 4, 2008, Monterey County, California. Notary: John McNally, Commission \#1607873.}

\vspace{1.5em}

% Document B
\noindent\rule{\textwidth}{0.5pt}\\[0.3em]
{\bfseries Document B-2: Last Will and Testament of Judy Brakebill Jones}\\[0.3em]
\rule{\textwidth}{0.5pt}

\vspace{0.5em}

\noindent\textit{Key Provision -- Article V: Fiduciaries (Page 3 of 9):}

\begin{quote}
``A. \underline{Personal Representatives}: I appoint \textbf{Eric Brakebill Jones} of San Francisco, California and \textbf{Heidi Jones Blanchard} of Chico, California as \textbf{Co-Personal Representatives} of this Will. In the event one should be or become unable or unwilling for any reason to serve as such Personal Representative, the other shall serve alone.

B. \underline{Waiver of Bond}: I direct that no Personal Representative, Trustee or Guardian named in this Article shall be required to furnish any bond or other security in any jurisdiction for the faithful performance of his duties as such, the same being specifically waived hereby.''
\end{quote}

\newpage

% Document C - CRITICAL
\noindent\rule{\textwidth}{0.5pt}\\[0.3em]
{\bfseries Document B-3: Certified Abstract of the Judy Brakebill Jones 2008 Revocable Trust}\\[0.3em]
{\bfseries\textcolor{red}{[CRITICAL EVIDENCE]}}\\[0.3em]
\rule{\textwidth}{0.5pt}

\vspace{1em}

\begin{center}
\fbox{\parbox{5.5in}{
\centering
\textbf{CERTIFIED ABSTRACT OF THE JUDY BRAKEBILL JONES 2008 REVOCABLE TRUST}\\[0.5em]
STATE OF CALIFORNIA\\
COUNTY OF MONTEREY
}}
\end{center}

\vspace{1em}

\noindent The UNDERSIGNED, being duly sworn, deposes and certified:

\vspace{0.5em}

\begin{quote}
Declaration of Trust is entitled \textbf{THE JUDY BRAKEBILL JONES 2008 REVOCABLE TRUST}\\
Settlor and Trustee: \textbf{JUDY LEE BRAKEBILL JONES}\\
Date of creation: \textbf{March 18, 2008}\\
\textbf{First Successor Trustee: ERIC BRAKEBILL JONES}\\
Second Successor Trustee: HEIDI JONES BLANCHARD
\end{quote}

\vspace{1em}

\noindent\textit{Key Provision -- Paragraph 3 (CRITICAL):}

\begin{quote}
``3. Settlor is empowered to designate trustees and successor trustees, and has appointed \textbf{ERIC BRAKEBILL JONES as successor trustee}, and should the named successor trustee become unable because of death, incapacity, or any other cause to serve before the natural termination of all the trust(s), \textbf{then HEIDI JONES BLANCHARD shall serve as the successor trustee}.''
\end{quote}

\vspace{1em}

\noindent\textit{Certification:}

\begin{quote}
``I certify under the laws of the State of California that this Abstract of the Judy Brakebill Jones 2008 Revocable Trust is true and correct to the best of my knowledge.''
\end{quote}

\vspace{0.5em}
\noindent\textit{Dated: April 4, 2008. Signed by JUDY LEE BRAKEBILL JONES, aka JUDY BRAKEBILL JONES, aka JUDY BRAKEBILL JONES LASHER, aka JUDY LEE JONES, Grantor/Settlor/Trustor/Trustee.}

\vspace{0.5em}
\noindent\textit{Notarization: April 4, 2008, Monterey County. Notary: John McNally.}

\vspace{2em}

% ═══════════════════════════════════════════════════════════════════════════════
% EVIDENTIARY SIGNIFICANCE
% ═══════════════════════════════════════════════════════════════════════════════

\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}\\[0.3em]
{\large\bfseries\textcolor{NavyHeader}{EVIDENTIARY SIGNIFICANCE}}\\[0.3em]
\noindent\textcolor{NavyHeader}{\rule{\textwidth}{1pt}}

\vspace{0.5em}

\begin{enumerate}
    \item \textbf{Document Possession:} Heidi Blanchard was in possession of the complete estate planning documents within 3 days of the decedent's death (April 4, 2025).

    \item \textbf{Trustee Order:} The Certified Abstract unambiguously establishes Eric Brakebill Jones as \textbf{First} Successor Trustee, with Heidi Jones Blanchard as \textbf{Second} Successor Trustee.

    \item \textbf{Heidi's Acknowledgment:} In her SMS at 1:50 PM, Heidi explicitly acknowledged: ``it says that you are a successor trustee and if you are unable to be successor trustee then Heidi Jones Blanchard she serve.''

    \item \textbf{Contradiction to Petition:} This evidence directly contradicts the Petition for Probate of Lost Will (Case No. 25PR000590), which claims the identity of the Executor is ``unknown.''
\end{enumerate}

% ═══════════════════════════════════════════════════════════════════════════════
% END OF EXHIBIT
% ═══════════════════════════════════════════════════════════════════════════════

\vfill

\begin{center}
\rule{3in}{1pt}\\[0.5em]
{\bfseries END OF EXHIBIT B}\\[0.3em]
\rule{3in}{1pt}
\end{center}

\end{document}
